The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2018-08-14 script/de/chapters/digitalsignatures.tex
CT book (de+en): Corrected some more broken links (also in bib files). Now all should work again.

  Mit CT1\index{CT1} können Sie den Geburtstagsangriff
  \index{Angriff!Geburtstagsangriff} auf digitale Signaturen
  nachvollziehen:\\
  über das Menü {\bf Analyse \textbackslash{} Hashverfahren
  \textbackslash{} Angriff auf den Hashwert der digitalen Signatur}.\\
  CT2\index{CT2} enthält einen MD5-Kollisionsgenerator.
  }
oder \index{RIPEMD-160} RIPEMD-160\footnote{%
  RIPEMD-160, RIPEMD-128 und die optionale Erweiterung RIPEMD-256 haben
  Object Identifier, definiert von der ISO-identifizierten Organisation
  TeleTrusT, sowohl für Hashverfahren als auch in Kombination mit RSA.
  RIPEMD-160 ist Teil des internationalen ISO/IEC-Standards
  ISO/IEC 10118-3:1998 für dedizierte Hashfunktionen, zusammen mit
  RIPEMD-128 and SHA-1. Weitere Details:\\
- \url{http://www.esat.kuleuven.ac.be/~bosselae/ripemd160.html}\\
- \url{http://www.ietf.org/rfc/rfc2857.txt} (``The Use of HMAC-RIPEMD-160-96
   within ESP and AH'').
  }%
) vertraut.

@@

Weitere Informationen zu diesem Thema finden sich z.B. in dem Artikel
\glqq Hash mich -- Konsequenzen der erfolgreichen Angriffe auf SHA-1\grqq\
von Reinhard Wobst und Jürgen Schmidt\footnote{%
      \url{https://www.heise.de/security/artikel/56555}.\\
  Weitere Quellen sind z.B.:\\
      % Toter Link: \url{http://www.bsi.bund.de/esig/basics/techbas/krypto/index.htm}\\
      \url{https://csrc.nist.gov/groups/ST/toolkit/index.html}.
}
  von Heise Security.

>>>>

  Mit CT1\index{CT1} können Sie den Geburtstagsangriff
  \index{Angriff!Geburtstagsangriff} auf digitale Signaturen
  nachvollziehen:\\
  über das Menü {\bf Analyse \textbackslash{} Hashverfahren
  \textbackslash{} Angriff auf den Hashwert der digitalen Signatur}.\\
  CT2\index{CT2} enthält einen MD5-Kollisionsgenerator.
  }
oder \index{RIPEMD-160} RIPEMD-160\footnote{%
  RIPEMD-160, RIPEMD-128 und die optionale Erweiterung RIPEMD-256 haben
  Object Identifier, definiert von der ISO-identifizierten Organisation
  TeleTrusT, sowohl für Hashverfahren als auch in Kombination mit RSA.
  RIPEMD-160 ist Teil des internationalen ISO/IEC-Standards
  ISO/IEC 10118-3:1998 für dedizierte Hashfunktionen, zusammen mit
  RIPEMD-128 and SHA-1. Weitere Details:\\
%% BE_Link umgeleitet: - \url{http://www.esat.kuleuven.ac.be/~bosselae/ripemd160.html}\\
- \url{https://homes.esat.kuleuven.be/~bosselae/ripemd160.html}\\
- \url{http://www.ietf.org/rfc/rfc2857.txt} (``The Use of HMAC-RIPEMD-160-96
   within ESP and AH'').
  }%
) vertraut.

@@

Weitere Informationen zu diesem Thema finden sich z.B. in dem Artikel
% BE: the \ after \grqq avoids that "(2005" follows without a blank. A "~" could do it too.
\glqq Konsequenzen der erfolgreichen Angriffe auf SHA-1\grqq\
(2005) von Reinhard Wobst und Jürgen Schmidt\footnote{%
      \url{https://www.heise.de/security/artikel/Konsequenzen-der-erfolgreichen-Angriffe-auf-SHA-1-270648.html}.\\
  Weitere Quellen sind z.B.:\\
      % Toter Link: \url{http://www.bsi.bund.de/esig/basics/techbas/krypto/index.htm}\\
      \url{https://csrc.nist.gov/groups/ST/toolkit/index.html}.
}
  von Heise Security.

### 2018-08-14 script/en/chapters/digitalsignatures.tex
CT book (de+en): Corrected some more broken links (also in bib files). Now all should work again.

  With CT1\index{CT1} you can comprehend the birthday attack
  \index{attack!birthday} on digital signatures:\\
  using the menu {\bf Analysis \textbackslash{} Hash \textbackslash{} 
  Attack on the Hash Value of the Digital Signature}.\\
  CT2\index{CT2} contains an MD5 collider.
  }  
or \index{RIPEMD-160} RIPEMD-160\footnote{%
  RIPEMD-160, RIPEMD-128 and the optional extension RIPEMD-256 have object
  identifiers defined by the ISO-identified organization TeleTrusT, both 
  as hash algorithm and in combination with RSA.
  RIPEMD-160 is also part of the ISO/IEC international standard 
  ISO/IEC 10118-3:1998 on dedicated hash functions, together with 
  RIPEMD-128 and SHA-1.
  Further details:\\
- \url{http://www.esat.kuleuven.ac.be/~bosselae/ripemd160.html}\\
- \url{http://www.ietf.org/rfc/rfc2857.txt} (``The Use of HMAC-RIPEMD-160-96
   within ESP and AH'').
  }%
) were trusted.

@@

%% BE_8.8.18: Englische Fassung von heise.de nicht mehr erreichbar.
%% Zumindest nicht die bisher angegebene Nummer.
%% ``Hash cracked -- The consequences of the successful attacks on SHA-1''
%%      \url{http://www.heise.de/security/artikel/56634}.\\
Further information about this topic can be found in the article
``Consequences of the successful attacks on SHA-1''
by Reinhard Wobst and J\"urgen Schmidt\footnote{% 
      \url{https://www.heise.de/security/artikel/Consequences-of-the-successful-attacks-on-SHA-1-270650.html}.\\
  Further references are e.g.:\\
      \url{https://csrc.nist.gov/groups/ST/toolkit/index.htmll}.
} 
  by Heise Security.

>>>>

  With CT1\index{CT1} you can comprehend the birthday attack
  \index{attack!birthday} on digital signatures:\\
  using the menu {\bf Analysis \textbackslash{} Hash \textbackslash{} 
  Attack on the Hash Value of the Digital Signature}.\\
  CT2\index{CT2} contains an MD5 collider.
  }  
or \index{RIPEMD-160} RIPEMD-160\footnote{%
  RIPEMD-160, RIPEMD-128 and the optional extension RIPEMD-256 have object
  identifiers defined by the ISO-identified organization TeleTrusT, both 
  as hash algorithm and in combination with RSA.
  RIPEMD-160 is also part of the ISO/IEC international standard 
  ISO/IEC 10118-3:1998 on dedicated hash functions, together with 
  RIPEMD-128 and SHA-1.
  Further details:\\
- \url{https://homes.esat.kuleuven.be/~bosselae/ripemd160.html}\\
- \url{http://www.ietf.org/rfc/rfc2857.txt} (``The Use of HMAC-RIPEMD-160-96
   within ESP and AH'').
  }%
) were trusted.

@@

%% BE_8.8.18: Englische Fassung von heise.de nicht mehr erreichbar.
%% Zumindest nicht die bisher angegebene Nummer.
%% ``Hash cracked -- The consequences of the successful attacks on SHA-1''
%%      \url{http://www.heise.de/security/artikel/56634}.\\
Further information about this topic can be found in the article
``Consequences of the successful attacks on SHA-1''
(2005) by Reinhard Wobst and J\"urgen Schmidt\footnote{% 
      \url{https://www.heise.de/security/artikel/Consequences-of-the-successful-attacks-on-SHA-1-270650.html}.\\
  Further references are e.g.:\\
      \url{https://csrc.nist.gov/groups/ST/toolkit/index.htmll}.
} 
  by Heise Security.
